Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
review Robust Synthesis of FWL Digital Controllers

To the authors' knowledge, there is no existing work on the automatic
synthesis of fixed point digital controllers considering FWL effects.  Parameter
synthesis tools such as~\cite{cimatti2013parameter} use bounded model
checking and fixed point computations to find parameters based on user
defined specifications, but they often operate in the continuous domain and
are ill-suited for robust analysis since they have no direct means of
evaluating robustness.  Other tools such as~\cite{economakos2016automated}
are directly aimed at robust stability problems but fail to explore the
effects of FWL in their implementation.  In order to provide a correct by
design controller, \cite{alur2016compositional} requires a user-defined
finite state abstraction to synthesise a digital controller based on high
level specifications.  Whilst this approach directly overcomes the
challenges presented by the FWL problem, it still requires error-prone user
intervention.  A different solution that looks at the other end of the scale
is an approach that synthesises word lengths for know problems as developed
in \cite{jha2013swati}, however this provides neither an optimal word
synthesis nor a comprehensive solution for the problem.  It is from this
vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.

>>>>

Given the current knowledge in control system's synthesis, there is no other 
existing study on the automatic synthesis of fixed-point digital controllers 
considering FWL effects.  Parameter synthesis tools such as~\cite{cimatti2013parameter} 
use bounded model checking and fixed-point computations to find parameters based on user
defined specifications, but they often operate in the continuous domain and
are ill-suited for robust analysis since they have no direct means of
evaluating robustness.  Other tools such as~\cite{economakos2016automated}
are directly aimed at robust stability problems, but they fail to explore the
effects of FWL in their implementation.  In order to provide a correct by
design digital controller, \cite{alur2016compositional} requires a user-defined
finite state abstraction to synthesise a digital controller based on high
level specifications.  Whilst this approach directly overcomes the
challenges presented by the FWL problem, it still requires error-prone user
intervention.  A different solution that looks at the other end of the scale
is an approach that synthesises word lengths for known problems as developed
in \cite{jha2013swati}; however, this provides neither an optimal word
synthesis nor a comprehensive solution for the problem.  It is from this
vacuum that we seek to explore a CEGIS approach to FWL controller synthesis.
